Exploring probability distributions for bivariate temporal granularities

### 2019-10-30 main.Rmd
making changes to circular granularity definition

A linear granularity, as defined by [@Bettini1998-ed], is essentially a mapping of the index set to subsets of the bottom granularity. Here, the domain is the index set and range is subsets of bottom granularity. Circular granularity, joining two linear granularities, therefore is a mapping between these two subsets of bottom granularity. They also accomodate periodicity and hence the smaller subsets of bottom granularity are repeating themselves within the larger subsets of bottom granularity. We use modular arithmetic to define circular granularity and use the following definitions:

@@

**Definition:** A **circular granularity** $C$ with a modular period m is defined to be a mapping from the integers $Z$ (Index Set) to $Z_m$, such that $C(s) = (s\mod m)$ for $s \in Z$.

>>>>

Suppose we have a tsibble with a time index in one column and keys and variables in other columns.

A time domain, as defined by Bettini, is essentially a mapping of row numbers (the index set) to the time index.

A linear granularity is a mapping of row numbers to subsets of the time domain. For example, if the time index is days, then a linear granularity might be weeks, months or years.  Circular granularity, joining two linear granularities, therefore is a mapping between these two subsets of time domain. We use modular arithmetic to define circular granularity and use the following definitions:

<!-- A linear granularity, as defined by [@Bettini1998-ed], is essentially a mapping of the index set to subsets of linear bottom granularity. Here, the domain is the index set and range contains subsets of linear bottom granularity. Circular granularity, joining two linear granularities, therefore is a mapping between these two subsets of linear bottom granularity. We use modular arithmetic to define circular granularity and use the following definitions: -->

<!-- They also accomodate periodicity and hence the smaller subsets of bottom granularity are repeating themselves within the larger subsets of bottom granularity.  -->

@@

**Definition:** A **circular granularity** $C$, joining two linear granularity with a modular period m is defined to be a mapping from the integers $Z$ (Index Set) to $Z_m$, such that

$C(s) = (s\mod m)$ for $s \in Z$.
